18.821 Project 2

### 2014-10-27 paper/paper.tex
S4 conjectures

@@

>>>>

\subsection{Flipping}

@@

In this section we will present our findings and conjectures about sequences $s_n(\pi)$ for $\pi\in S_4$. We computed values up to $s_{10}$. It appears that there are three sequences that appear, and we have sorted the permutations according to which sequence they produce and paired them with their flips.

We define the following sequences based on the first 8 terms:
$$
A:=1,2,6,23,103,512,2740,15485,91245\ldots
$$
$$
B:=1,2,6,23,103,513,2761,15767,94359\ldots
$$
$$
C:=1,2,6,23,103,513,2762,15793,94776\ldots
$$

The table below lists the elements of $S_4$ generate sequences $A,B,C$ for the first 8 terms.

\begin{center}
\begin{tabular}{|c|c|c|}
B &A&C\\
\hline
1234, 4321&4132, 1423&4231,1324\\
1243, 4312&4213, 1342&\\
1432, 4123&2431,3124&\\
2134, 3421&2413, 3142&\\
2143, 3412&2314, 3241&\\
2341, 3214&&\\
\end{tabular}
\end{center}

There is no guarantee that these sequences will not diverge and produce more than three distinct sequences, however for now we hypothesize that $A$, $B$, and $C$ are the only sequences that arise for $s_n(\pi)$ with $\pi\in S_4$. Assuming this hypothesis, if we write each length four permutation in cycle notation, a pattern begins to emerge.

\begin{center}
\begin{tabular}{|c|c|c|}
B &A&C\\
\hline
(1),(14)(23)&(243),(142)&(23),(14)\\
(34),(1423)&(234),(143)&\\
(24),(1432)&(124),(132)&\\
(12),(1324)&(123),(134)&\\
(12)(34),(13)(24)&(1243),(1342)&\\
(1234),(13)&&\\
\end{tabular}
\end{center}

So we conjecture that sequence $A$ is characterized by elements of $S_4$ that are three cycles or four cycles when written in cycle notation. Sequence $B$ seems to be characterized by either a pair of disjoint two cycles paired with a flip that is a 2-cycle, or a single 4-cycle paired with a flip that is a 2-cycle. Sequence $C$ appears to be characterized by a 2-cycle paired with a 2-cycle as a flip.
